% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Borsuk, Amaranth. 2018. \emph{The Book}. MIT Press.

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Card, Stuart K, Allen Newell, και Thomas P Moran. 1983. \emph{The
Psychology of Human-Computer Interaction}. L. Erlbaum Associates Inc.

Carlston, DG. 1985. {`Software People: inside the computer business'}.
New York: Prentice Hall.

Engelbart, Douglas C. 1962. \emph{Augmenting human intellect: A
conceptual framework}. SRI, Menlo Park, CA.

Freiberger, Paul, και Michael Swaine. 1984. \emph{Fire in the Valley:
the making of the personal computer}. McGraw-Hill, Inc.

Hertzfeld, Andy. 2004. \emph{Revolution in The Valley: The Insanely
Great Story of How the Mac Was Made}. " O'Reilly Media, Inc.".

Hiltzik, Michael. 1999. {`Dealers of Lightning: Xerox PARC and the
Dawning of the Computer Age'}.

Johnson, Jeff, Teresa L. Roberts, William Verplank, David Canfield
Smith, Charles H. Irby, Marian Beard, και Kevin Mackey. 1989. {`The
xerox star: A retrospective'}. \emph{Computer} 22 (9): 11--26.

Kay, Alan C. 1993. {`The early history of Smalltalk'}. \emph{ACM SIGPLAN
Notices} 28 (3): 69--95.

Lanier, Jaron. 2014. \emph{Who owns the future?} Simon; Schuster.

Licklider, Joseph Carl Robnett. 1960. {`Man-computer symbiosis'}.
\emph{IRE transactions on human factors in electronics}, τχ. 1: 4--11.

Papert, Seymour. 1980. \emph{Mindstorms: children, computers, and
powerful ideas}. Basic Books, Inc.

Raskin, Jef. 2000. \emph{The humane interface: new directions for
designing interactive systems}. Addison-Wesley Professional.

Rheingold, Howard. 2000. \emph{Tools for thought: The history and future
of mind-expanding technology}. MIT Press.

Smith, Douglas K, και Robert C Alexander. 1999. \emph{Fumbling the
future: How Xerox invented, then ignored, the first personal computer}.
iUniverse.

Waldrop, M Mitchell. 2001. \emph{The dream machine: JCR Licklider and
the revolution that made computing personal}. Viking Penguin.

Weizenbaum, Joseph. 1976. \emph{Computer power and human reason: From
judgment to calculation.} WH Freeman \& Co.

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Buxton, Bill. 2010. \emph{Sketching user experiences: getting the design
right and the right design}. Morgan kaufmann.

Card, Stuart K, William K English, και Betty J Burr. 1978. {`Evaluation
of mouse, rate-controlled isometric joystick, step keys, and text keys
for text selection on a CRT'}. \emph{Ergonomics} 21 (8): 601--13.

Card, Stuart K, Thomas P Moran, και Allen Newell. 2018. \emph{The
psychology of human-computer interaction}. Crc Press.

Carroll, John M. 2000. \emph{Making use: scenario-based design of
human-computer interactions}. MIT press.

Moggridge, Bill. 2007. \emph{Designing interactions}. MIT press
Cambridge, MA.

Norman, Don. 2013. \emph{The design of everyday things: Revised and
expanded edition}. Basic books.

Papanek, Victor, και R Buckminster Fuller. 1972. \emph{Design for the
real world}. Thames; Hudson London.

Pering, Celine. 2002. {`Interaction design prototyping of communicator
devices: Towards meeting the hardware-software challenge'}.
\emph{interactions} 9 (6): 36--46.

Thackara, John. 2006. \emph{In the bubble: designing in a complex
world}. MIT press.

Winograd, Terry κ.ά. 1996. \emph{Bringing design to software}.
\(\{\)Addison-Wesley Professional\(\}\).

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Garrett, Jesse James. 2010. \emph{Elements of user experience, the:
user-centered design for the web and beyond}. Pearson Education.

Hiltzik, Michael. 1999. {`Dealers of Lightning: Xerox PARC and the
Dawning of the Computer Age'}.

Igoe, Tom. 2007. \emph{Making things talk: Practical methods for
connecting physical objects}. " O'Reilly Media, Inc.".

McEwen, Adrian, και Hakim Cassimally. 2013. \emph{Designing the internet
of things}. John Wiley \& Sons.

Norman, Don. 2013. \emph{The design of everyday things: Revised and
expanded edition}. Basic books.

Norman, Donald A. 2004. \emph{Emotional design: Why we love (or hate)
everyday things}. Basic Civitas Books.

O'Sullivan, Dan, και Tom Igoe. 2004. \emph{Physical computing: sensing
and controlling the physical world with computers}. Course Technology
Press.

Shneiderman, Ben, και Pattie Maes. 1997. {`Direct manipulation vs.
interface agents'}. \emph{interactions} 4 (6): 42--61.

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Andrew, Hunt, και Thomas David. 2000. {`The Pragmatic Programmer: From
Journeyman to Master'}. Addison Wesley Longman, Redwood City.

Banzi, Massimo, και Michael Shiloh. 2014. \emph{Getting started with
Arduino: the open source electronics prototyping platform}. Maker Media,
Inc.

Graham, Paul. 2004. \emph{Hackers \& painters: big ideas from the
computer age}. " O'Reilly Media, Inc.".

Grudin, Jonathan. 1990. {`The computer reaches out: the historical
continuity of interface design'}. Στο \emph{Proceedings of the SIGCHI
conference on Human factors in computing systems}, 261--68. ACM.

Ingalls, Daniel. 2020. {`The evolution of Smalltalk: from Smalltalk-72
through Squeak'}. \emph{Proceedings of the ACM on Programming Languages}
4 (HOPL): 1--101.

Markoff, John. 2005. \emph{What the dormouse said: How the sixties
counterculture shaped the personal computer industry}. Penguin.

McConnell, Steve. 2004. \emph{Code complete}. Pearson Education.

Noble, Joshua. 2009. \emph{Programming interactivity: a designer's guide
to Processing, Arduino, and OpenFrameworks}. " O'Reilly Media, Inc.".

Olsen, Dan. 2009. \emph{Building interactive systems: principles for
human-computer interaction}. Cengage Learning.

Reas, Casey, και Ben Fry. 2007. \emph{Processing: a programming handbook
for visual designers and artists}. 6812. Mit Press.

Thimbleby, H. 2007. \emph{press on: Principles of Interaction
Programming}. MIT Press, Cambridge.

Victor, Bret. 2012. {`Learnable programming: Designing a programming
system for understanding programs'}. 2012.
\url{http://worrydream.com/LearnableProgramming}.

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Fogg, BJ. 2003. \emph{Persuasive Technology: Using Computers to Change
What We Think and Do}. Morgan Kaufmann.

Kaptelinin, Victor, και Mary Czerwinski. 2007. \emph{Beyond the desktop
metaphor: designing integrated digital work environments}. Τ. 1. The MIT
Press.

Krueger, M. W. 1991. \emph{Artificial Reality II}. Addison-Wesley.

Laurel, Brenda. 2013. \emph{Computers as theatre}. Addison-Wesley.

Levy, Steven. 1984. \emph{Hackers: Heroes of the computer revolution}.
Τ. 14. Anchor Press/Doubleday Garden City, NY.

Markoff, John. 2005. \emph{What the dormouse said: How the sixties
counterculture shaped the personal computer industry}. Penguin.

McCullough, Malcolm. 1998. \emph{Abstracting craft: The practiced
digital hand}. MIT press.

Norman, Don. 2014. \emph{Things that make us smart: Defending human
attributes in the age of the machine}. Diversion Books.

Norman, Donald A. 2004. \emph{Emotional design: Why we love (or hate)
everyday things}. Basic Civitas Books.

Reeves, Byron, και Clifford Ivar Nass. 1996. \emph{The media equation:
How people treat computers, television, and new media like real people
and places.} Cambridge university press.

Rheingold, Howard. 2000. \emph{The Virtual Community: Homesteading on
the Electronic Frontier}. MIT press.

Weizenbaum, Joseph. 1976. \emph{Computer power and human reason: From
judgment to calculation.} WH Freeman \& Co.

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Baecker, Ronald M. 1993. \emph{Readings in groupware and
computer-supported cooperative work: Assisting human-human
collaboration}. Elsevier.

Barnet, Belinda. 2013. \emph{Memory machines: The evolution of
hypertext}. Anthem Press.

Berners-Lee, Tim. 1996. {`WWW: Past, present, and future'}.
\emph{Computer} 29 (10): 69--77.

Bolt, Richard A. 1978. {`Spatial data management system'}. MASSACHUSETTS
INST OF TECH CAMBRIDGE ARCHITECTURE MACHINE GROUP.

Bush, Vannevar κ.ά. 1945. {`As we may think'}. \emph{The atlantic
monthly} 176 (1): 101--8.

Garrett, Jesse James. 2010. \emph{Elements of user experience, the:
user-centered design for the web and beyond}. Pearson Education.

Licklider, Joseph Carl Robnett. 1960. {`Man-computer symbiosis'}.
\emph{IRE transactions on human factors in electronics}, τχ. 1: 4--11.

Malone, Thomas W, και Kevin Crowston. 1994. {`The interdisciplinary
study of coordination'}. \emph{ACM Computing Surveys (CSUR)} 26 (1):
87--119.

Nelson, Theodor H. 1974. {`Computer lib/Dream machines'}.

Nelson, Theodor H κ.ά. 2010. \emph{POSSIPLEX: movies, intellect,
creative control, my computer life and the fight for civilization: an
autobiography of Ted Nelson}. Mindful Press.

Packer, Randall, και Ken Jordan. 2002. \emph{Multimedia: from Wagner to
virtual reality}. WW Norton \& Company.

Shiffman, Daniel. 2009. \emph{Learning Processing: a beginner's guide to
programming images, animation, and interaction}. Morgan Kaufmann.

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Denning, Peter J, και Robert M Metcalfe. 1998. \emph{Beyond calculation:
The next fifty years of computing}. Springer Science \& Business Media.

Engelbart, Douglas. 1988. {`The augmented knowledge workshop'}. Στο
\emph{A history of personal workstations}, 185--248.

Freiberger, Paul, και Michael Swaine. 1984. \emph{Fire in the Valley:
the making of the personal computer}. McGraw-Hill, Inc.

Goldberg, Adele, επιμ. 1988. \emph{A History of Personal Workstations}.
New York, NY, USA: Association for Computing Machinery.

Hertzfeld, Andy. 2004. \emph{Revolution in The Valley
{{[}}Paperback{{]}}: The Insanely Great Story of How the Mac Was Made}.
" O'Reilly Media, Inc.".

Kay, Alan, και Adele Goldberg. 1977. {`Personal dynamic media'}.
\emph{Computer} 10 (3): 31--41.

Kernighan, Brian W. 2019. \emph{UNIX: A History and a Memoir}. Kindle
Direct Publishing.

Lanier, Jaron. 2017. \emph{Dawn of the new everything: Encounters with
reality and virtual reality}. Henry Holt; Company.

Laurel, Brenda. 2013. \emph{Computers as theatre}. Addison-Wesley.

Nelson, Ted. 2008. \emph{Geeks Bearing Gifts}. Mindful Pr.

Sellen, Abigail J, και Richard HR Harper. 2003. \emph{The myth of the
paperless office}. MIT press.

Waldrop, M Mitchell. 2001. \emph{The dream machine: JCR Licklider and
the revolution that made computing personal}. Viking Penguin.

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

Bardini, Thierry. 2000. \emph{Bootstrapping: Douglas Engelbart,
coevolution, and the origins of personal computing}. Stanford University
Press.

Bolter, Jay David, και Richard Grusin. 2000. \emph{Remediation:
Understanding new media}. mit Press.

Engelbart, Douglas C. 1962. \emph{Augmenting human intellect: A
conceptual framework}. SRI, Menlo Park, CA.

Gildall, Gary. 1993. \emph{Computer Connections: People, Places, and
Events in the Evolution of the Personal Computer Industry}. Unpublished.

Hiltzik, Michael. 1999. {`Dealers of Lightning: Xerox PARC and the
Dawning of the Computer Age'}.

Ihde, Don. 2012. \emph{Technics and praxis: A philosophy of technology}.
Τ. 24. Springer Science \& Business Media.

Ingalls, Daniel. 2020. {`The evolution of Smalltalk: from Smalltalk-72
through Squeak'}. \emph{Proceedings of the ACM on Programming Languages}
4 (HOPL): 1--101.

Kay, Alan C. 1993. {`The early history of Smalltalk'}. \emph{ACM SIGPLAN
Notices} 28 (3): 69--95.

Lakoff, George, και Mark Johnson. 2008. \emph{Metaphors we live by}.
University of Chicago press.

Lanier, Jaron. 2010. \emph{You are not a gadget: A manifesto}. Vintage.

Mumford, Lewis. 2010. \emph{Technics and civilization}. University of
Chicago Press.

Nelson, Theodor H. 2010. \emph{POSSIPLEX: movies, intellect, creative
control, my computer life and the fight for civilization: an
autobiography of Ted Nelson}. Mindful Press.

Raskin, Jef. 2000. \emph{The humane interface: new directions for
designing interactive systems}. Addison-Wesley Professional.

Roszak, Theodore. 1986. \emph{From Satori to Silicon Valley: San
Francisco and the American Counterculture}. Don't Call It Frisco Press.

Shasha, Dennis, και Cathy Lazere. 1998. \emph{Out of their minds: the
lives and discoveries of 15 great computer scientists}. Springer Science
\& Business Media.

Wirth, Niklaus, και Jürg Gutknecht. 1992. \emph{Project Oberon}.
Addison-Wesley Reading.

\end{document}
